A Plasma Torus Around a Young Low-Mass Star

### 2025-06-09 paper/ms.tex
update

  The analyses in this article used data from TESS.  \added{The
  2-minute cadence observations from Sectors 41 \& 48 were from TESS
  DDT039 (PI: M.~Kunimoto) and the observations from Sector 75 were
  from TESS G06030 (PI: L.~Bouma).}
  The TESS data can be accessed \added{through MAST }via
  DOI\,\dataset[10.17909/t9-nmc8-f686]{https://doi.org/10.17909/t9-nmc8-f686}.
  Funding for the TESS mission is provided by NASA’s Science Mission
  directorate.
  TESS is a product of millions of hours of work by thousands of
  people, and we thank the TESS team for their efforts to make the
  mission a continued success.
  The HIRES data were obtained at the Keck Observatory, which exists
  through a similar scale of community effort.
  We recognize the importance that the summit of Maunakea has always
  had within the indigenous Hawaiian community, and we are grateful
  for the opportunity to conduct observations from this mountain.
\end{acknowledgements}

>>>>

  The analyses in this article used data from TESS \citep{TESS2min}.  \added{The
  2-minute cadence observations from Sectors 41 \& 48 were from TESS
  DDT039 (PI: M.~Kunimoto) and the observations from Sector 75 were
  from TESS G06030 (PI: L.~Bouma).}
  Funding for the TESS mission is provided by NASA’s Science Mission
  directorate.
  TESS is a product of millions of hours of work by thousands of
  people, and we thank the TESS team for their efforts to make the
  mission a continued success.
  The HIRES data were obtained at the Keck Observatory, which exists
  through a similar scale of community effort.
  We recognize the importance that the summit of Maunakea has always
  had within the indigenous Hawaiian community, and we are grateful
  for the opportunity to conduct observations from this mountain.
\end{acknowledgements}
